%_______________________________________________________________________________
% main.tex

\input{preamble12.tex}
\hypersetup{%
    pdfauthor={Mike Pierce}%
   ,pdftitle={Life Expectancy}%
   ,pdfkeywords={Pierce,CMU,Colorado,College Algebra,113}%
   ,pageanchor=false%
}
\geometry{
    margin=0.67in%
}
\usepackage{fourier}
\usepackage[default]{comicneue}
\input{accessible-colors.tex}
\input{newcommand.tex}
\input{newenvironment.tex}
\pagenumbering{gobble}
\usepackage{pagegrid}
\pagegridsetup{
    step=0.5in
    ,firstcolor=blue
    ,secondcolor=orange
    ,foreground=true
    ,disable
}


\begin{document}

The table in the right margin gives the projected life expectancy (life span)
of a person born in the United States for select birth years
from 1920 and through 2018 according to the 
CDC\footnote{\href{https://www.cdc.gov/nchs/data-visualization/mortality-trends/}{cdc.gov/nchs/data-visualization/mortality-trends}}.

\vspace{-1em}

\begin{minipage}[t]{0.83\textwidth}
    \begin{enumerate}
        \item
    Using technology, perform regression to
            find a logarithmic function \(f(t) = a + b\ln(t)\) 
    that models the data,
    with \(t\) equal to \(0\) in 1900.

        \item
    Using technology, perform regression to
    find a power model \(g(t) = a\cdot t^b\) 
    that models the data,
    with \(t\) equal to \(0\) in 1900.

        \item
            Using technology,
    plot the graphs of each of these functions
    along with the data on the same set of axis
    and decide which model fits the data best. 
    On your plot make sure the domain of \(t\)
    matches up with the years 1920--2030.

\item 
    Between these two models, which one 
            predicts life expectancy will  increase \emph{more} in the future?
            I.e.~which of these models is more optimistic?

\item 
    What does the model that you decided 
            fits the data best predict your own life expectancy to be?

\item 
    What does the model that you decided 
            fits the data best predict 
            the life expectancy of a baby born today to be?

\item 
    What year does the logarithmic model
    predict life expectancy to be 80 years old?

\item 
    In the years since 2018, 
    life expectancy in the US has started to decline\footnotemark.
            This is suspected to be due to the \textsc{COVID}-19 pandemic.
            Someone born in the US in 2019, 2020, and 2021 
            has a life expectancy of 79 years, 77 years, and 76.1 years respectively.
            Add this new data to the data set.

            Both logarithmic and power functions are increasing functions.
            Since life expectancy is decreasing in recent years though,
            these functions may no longer provide the most accurate models.
            What's a type of function that more accurately models
            data that initially increases, but then begins to decrease?
            Using technology, perform regression to
            find such function \(h(t)\) 
            that models the data,
            again with \(t\) equal to \(0\) in 1900.

\item 
    What does this new model predict
            the life expectancy of a baby born today to be?
            How does this compare to the figure predicted
            by either your logarithmic or power model?

        \item
            Research: go online and see if you can find 
            \emph{reliable} life expectancy data for the year 2022.

    \end{enumerate}

\end{minipage}
\footnotetext{\href{https://www.npr.org/sections/health-shots/2022/08/31/1120192583/}{npr.org/sections/health-shots/2022/08/31/1120192583}}.
\hspace{1em}
\begin{minipage}[t]{0.12\textwidth}
    \par\begin{center}\begin{tabular}{m{1cm}|m{1cm}}
    Year & Life Span \\\hline
    1920 & 54.1 \\
        1925 & 60.6 \\
    1930 & 59.7 \\
        1935 & 63.9 \\
    1940 & 62.9 \\
        1945 & 65.9 \\
    1950 & 68.2 \\
    1955 & 69.6 \\
    1960 & 69.7 \\
    1965 & 70.2 \\
    1970 & 70.8 \\
    1975 & 72.6 \\
    1980 & 73.7 \\
    1985 & 74.7 \\
    %1988 & 74.9 \\
    %1989 & 75.2 \\
    1990 & 75.4 \\
    1992 & 75.8 \\
    1994 & 75.7 \\
    1996 & 76.1 \\
    1998 & 76.7 \\
    %1999 & 76.7 \\
    2000 & 76.8 \\
    2002 & 77.0 \\
    %2003 & 77.6 \\
    2004 & 77.5 \\
    2006 & 77.8 \\
    2008 & 78.2 \\
    2010 & 78.7 \\
    2011 & 78.7 \\
    2012 & 78.8 \\
    2013 & 78.8 \\
    2014 & 78.9 \\
    2015 & 78.7 \\
    2016 & 78.7 \\
    2017 & 78.6 \\
    2018 & 78.7
\end{tabular}\end{center}
\end{minipage}

\end{document}

